cvx-flats

### 2020-05-05 neurips-20/cvx-flats-statements.tex
Added a proof of calibrated implies indirect elicitation.

\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
\jessiet{Explain to reader why this is a good def. Made note in original doc.}
	A loss $L$ \emph{indirectly elicits} a property $\Gamma':\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \Gamma'_{\psi(r)}$.
\end{definition}

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a property $\gamma$, then they are calibrated with respect to $\gamma$.
	\jessie{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{...}
\end{proof}

\begin{theorem}\label{prop:consistent-implies-indir-elic}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or with respect to a loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
Proposition~\ref{prop:consistent-implies-calibrated} shows consistency (w.r.t. a property) implies calibration with respect to the same property.
Therefore it suffices to show calibration implies indirect elicitation.
\jessie{...}
%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
%Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e. the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
%
%Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
%\begin{align*}
%\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
%\end{align*}
%Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
\end{proof}

>>>>

\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
\jessiet{Explain to reader why this is a good def. Made note in original doc.}
	A loss $L$ \emph{indirectly elicits} a property $\gamma:\simplex \toto \R'$ if it elicits a property $\Gamma: \simplex \toto \R$ such that there is a function $\psi:\R \to \R'$ such that for all $r \in \R$, we have $\Gamma_r \subseteq \gamma_{\psi(r)}$.
\end{definition}

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a property $\gamma$, then they are calibrated with respect to $\gamma$.
	\jessie{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{ want to commit to definition of consistency first...}
\end{proof}

\begin{theorem}\label{prop:consistent-implies-indir-elic}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or with respect to a loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
Proposition~\ref{prop:consistent-implies-calibrated} shows consistency (w.r.t. a property) implies calibration with respect to the same property.
Therefore it suffices to show calibration implies indirect elicitation.
Fix $p \in \simplex$ such that $u \in \Gamma(p)$.
If $u \in \Gamma(p)$, then $L(u;p) - L(\Gamma(p); p) = 0$, and we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
As predicting $\gamma(p)$ yields the other side of the inequality, we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $\psi(u) \in \gamma(p)$.
Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.

%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass, allowing us to focus on conditional distributions $p \in \simplex$ such that $p = Pr[Y = y | X = x]$, allowing us to be agnostic to $\X$.
%Instead of focusing on sequences of optimal hypotheses, we can now focus on optimal reports when given $x \in \X$ if the hypothesis class $\F$ is sufficiently rich (i.e. the optimal hypothesis is in the hypothesis class for all $x \in \X$.)
%
%Consider $\Gamma := \prop{L}$ is given by $\Gamma(p) = \arginf_u \E_{Y \sim p} L(u, Y)$, so consistency with respect to $\ell$ yields 
%\begin{align*}
%\inf_u \E_{Y \sim p} L(u, Y) = \E_{Y \sim p} L(\Gamma(p), Y) &\implies \inf_r \E_{Y \sim p} \ell(r, Y) = \E_{Y \sim p} \ell(\psi \circ \Gamma(p), Y)~.~ 
%\end{align*}
%Since this is true for all $p \in \simplex$, then we have $L$ indirectly eliciting the property $\gamma$ by directly eliciting $\Gamma$ and using the link $\psi$.
\end{proof}
